The rest of this thesis is organized as follows. In \hyperref[ch:background]
{Chapter~\ref{ch:background}}, we provide background to various anomaly 
detection techniques, as well as randomization techniques. In order to provide 
the reader with an understanding of the background topics, a brief background is
given to various topics in linear algebra, vector calculus and graph theory. In
\hyperref[ch:reconfigurableComputing]{Chapter~\ref{ch:reconfigurableComputing}}, 
we provide an overview of reconfigurable computing, including an explanation of 
Field-Programmable Gate Arrays (FPGAs).

In \hyperref[ch:design] {Chapter~\ref{ch:design}}, we profile the execution of 
an anomaly detection algorithm and explore possible improvements to the 
algorithm, in particular by outsourcing various stages of the algorithm to an 
FPGA device. In \hyperref[ch:implementation]{Chapter~\ref{ch:implementation}}, 
we describe the implementation of the improved algorithm and detail the process 
that was followed in order to construct the hardware processing device. In 
\hyperref[ch:results]{Chapter~\ref{ch:results}}, we record results obtained by 
benchmarking the device that was previously designed and constructed, and 
comparing the expected improvements to the algorithm's execution with the 
measured results.

We conclude in \hyperref[ch:conclusions] {Chapter~\ref{ch:conclusions}} by 
reflecting upon the results obtained through this research, and making 
suggestions for further research in this topic.
