This appendix contains various source code that was used throughout the Thesis.
The source code listed in this section is not intended to be complete, but
rather contains some macros and functions that have not been defined in this
section. The code, however, should be clear in purpose and intention. The full
source code from can be freely downloaded from \gitRepoHTTP{} (over HTTP) or
\gitRepoSSH{} (over SSH).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MATLAB code
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{MATLAB code}
\label{sourceCode:matlab}
The original \software{MATLAB} code that was used in this Thesis is listed
below. This code was provided by \citeauthor{Khoa:2012}, but has been modified
slightly, mostly for stylistic and functional purposes.

The code below illustrates a single implementation of the
\command{TopN_Outlier_Pruning_Block} function --- namely, the \emph{sorted}
implementation. In this implementation, the array containing a vector's
$k$-nearest nearest neighbours is maintained in a sorted order in order to
facilitate future array insertions.

% TODO
\input{appendix/code-matlab}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% C code
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{C Code}
\label{sourceCode:c}
% TODO
\input{appendix/code-c}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AutoESL code
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{AutoESL Code}
\label{sourceCode:autoesl}
% TODO
\input{appendix/code-autoesl}