%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The Algorithm
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The Algorithm}
\begin{frame}{The Algorithm}{Anomaly Detection Using Commute Time}\relax
    {\tiny
        \begin{algorithm}[H]
            \input{chapter02/anomaly-detection_commute-time.algm}
        \end{algorithm}
    }

    \note<1>{The anomaly detection algorithm is described in the next two
        slides, however due to time constraints I will not discuss the algorithm
        in any great detail. Basically, the algorithm consists of:
    }

    \note<2>{Constructing the $k$-nearest neighbour graph for the input data
        set.}
    \note<3>{Using graph component sampling and eigenspace embedding to reduce
        the dimensionality of the data.}
    \note<4>{Reconstructing the $k$-nearest neighbour graph using the sampled
        data.}
    \note<5>{Computing the Laplacian matrix of the sampled graph and its $m$
        smallest eigenvectors.}
    \note<6>{Performing distance based anomaly detection.}

    \note<6>{From analysis of the run time performance of this anomaly detection
        algorithm, to be discussed later, the
        ``distance based anomaly detection'' stage of the algorithm was selected
        as a canditate for a hardware implementation.}
\end{frame}

\begin{frame}[shrink]{The Algorithm}{Outlier Pruning}\relax
    {\tiny
        \begin{algorithm}[H]
            \input{chapter04/top-n-outlier-pruning-block.algm}
        \end{algorithm}
    }

    \note{This slide describes the distance based anomaly detection method that
        is to be implemented in hardware. To aide in the understanding of this
        function, I will demonstrate an animation which clearly illustrates the
        anomaly detection function's execution.}
\end{frame}