This project could not have been completed without the guidance of my project
supervisor, \supervisorName{}. He always made himself available to assist me
with the understanding of many concepts, which were both new and unknown. His
expertise in the field was a great asset and greatly contributed to my own
understanding of the ideas explored in this thesis. His support and guidance was
invaluable, and were instrumental to the success of my project.

Much of the works completed during this project could not have been performed
without the prior research of \getPerson{Chawla} and \getPerson{Khoa}. Both were
generous enough to lend their own support and expertise in order to provide an
understanding of the implemented anomaly detection algorithm.

Additionally, I must thank \getPerson{Frechtling} for his assistance and advice
throughout the project. He assisted me with software packages including
\software{Xilinx\textsuperscript{\textregistered} AutoESL} and
\software{Altera\textsuperscript{\textregistered} ModelSim} (along with many
others), as well as offering valuable advice regarding my future professional
career.

Last but not least, none of this would have been possible without the support
and care of my family. My immediate family, to whom I deeply appreciate, always
has been a continuous source of support and encouragement throughout my
university degree. And I would like to express my gratitude to my girlfriend,
\getPerson{Heinrichs}, for her love, patience and support throughout the final
year of my university studies.